Error Correction in a Phenomenological Fibonacci Anyon Quantum Code

### 2014-08-19 ising/Fibonacci/about.tex

\documentclass[12pt]{article}
%\documentclass[11pt, twocolumn]{article}

@@

@@

\section{Braid group}

@@

\section{Fibonacci Anyons}

So we have a representation of the braid group.

\section{Curve Diagrams}

Given a topological space $X$ we define the {\it mapping class group} of $X$ as
the set of homeomorphisms $f:X\to X$ modulo isotopy

    % $$ MCG(X) := \{ f : X \to X \text{s.t.} f \text{is homeomorphism} \} / \sim_{\text{iso}} $$
    $$ MCG(X) := \{ f : X \to X \} / \sim_{\text{iso}}.$$

In particular we are interested in the $n$-punctured disc:

    $$ D_n := \mathZ^2 - n.$$

topologically this is a sphere with $n+1$ holes in it.

@@

Curve diagrams, see \cite{Dehornoy02}.

We verify the braid relations directly.

%
%\begin{center}
%%\includegraphics[width=0.5\textwidth]{mypicture.png}
%\includegraphics{fig00.eps}
%\end{center}

>>>>

\documentclass[12pt,a4paper]{article}
%\documentclass[11pt, twocolumn]{article}

\usepackage[paper=a4paper,dvips,top=1.5cm,left=1.5cm,right=1.5cm,
    foot=1cm,bottom=1.5cm]{geometry}

@@

%\def\heading #1{\noindent\underline{\Large\bf #1}}
\def\heading #1{\vskip 20pt \noindent\underline{\bf #1}\vskip 5pt}

@@

\heading{Braid group}

@@

\heading{Fibonacci Anyons}

So we have a (linear) representation of the braid group:

    $$ \kappa : B_n \to GL(F_n).$$

Where $F_n$ is the Hilbert state space of $n$ Fibonacci anyons with
trivial total charge.

\heading{Snake Diagrams}

%Given a topological space $X$ we define the {\it mapping class group} of $X$ as
%the set of homeomorphisms $f:X\to X$ modulo isotopy
%
%    % $$ MCG(X) := \{ f : X \to X \text{s.t.} f \text{is homeomorphism} \} / \sim_{\text{iso}} $$
%    $$ MCG(X) := \{ f : X \to X \} / \sim_{\text{iso}}.$$

Given a topological manifold $M$ we define the {\it mapping class group} of $M$ as
the set of homeomorphisms $f:M\to M$ modulo isotopy

    $$ MCG(M) := \{ f : M \to M \} / \sim_{\text{iso}}.$$

If $M$ has boundary $\partial M$ we require the homeomorphisms to
be the identity on $\partial M$.

In particular we are interested in
 the $n$-punctured disc.
This is a disc $D = \{ x\in \mathR^2 s.t. |x|\leq 1 \} $
with $n$ points removed:

    $$ D_n := D - Q_n,$$

where $Q_n$ is some finite subset of the interior of $D$.

%topologically this is a sphere with $n+1$ holes in it.

@@

We fix $Q_n$ to be the points $\{(0, i/(n+1)) for i=1,...n\}$
then we define the line $L = \{(0, x) s.t. |x|\leq 1\}.$
Given a representative $f$ of an element of $MCG(D_n)$
we define the
snake diagram as the
image of $L$ under $f$.

It is a theorem (see \cite{Dehornoy02}) that such snake diagrams
correspond uniquely to elements of the mapping class group, and
hence to the braid group $B_n$.

Here we verify the braid relations directly:

\begin{center}
%\includegraphics[width=0.5\textwidth]{mypicture.png}
\includegraphics[width=0.5\textwidth]{curve-braid.eps}
\end{center}

\heading{Pair-of-pants decompositions}

We measure charge in regions bounded by curves, ie. elements of
the first homology group $H_1(D_n).$
